Fifteen years of decentralization attempts

### 2014-03-20 table.tex
Add \xmark

		Gnutella & 2000 & x & \checkmark & \checkmark & x & x & x & x \\ \hline
		Freenet & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & \checkmark\\ \hline
		Tapestry & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & x \\ \hline
		Pastry & 2001 & x & \checkmark & \checkmark & \checkmark & x & x & x \\ \hline
		Anonymizing peer-to-peer proxy (AP3) & 2004 & x & x & x & ? & ? & ? & \checkmark\\ \hline
		Tarzan & 2002 & x & x & x & ? & ? & ? & \checkmark\\ \hline
		MorphMix & 2002 & x & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
		I2P & 2003 & x & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
		Salsa & 2006 & x & ? & ? & ? & ? & ? & ?\\ \hline
		Tribler & 2008 & x & \checkmark & \checkmark & ? & ? & ? & x\\ \hline
		Torks & 2009 & \checkmark & x & x & ? & ? & ? & \checkmark\\ \hline
		NISAN & 2009 & x & x & x & ? & ? & ? & \checkmark\\ \hline
    \end{longtable}
\end{center}

>>>>

		Gnutella & 2000 & \xmark & \checkmark & \checkmark & \xmark & \xmark & \xmark & \xmark \\ \hline
		Freenet & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \checkmark \\ \hline
		Tapestry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
		Pastry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
		Anonymizing peer-to-peer proxy (AP3) & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
		Tarzan & 2002 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
		MorphMix & 2002 & \xmark & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
		I2P & 2003 & \xmark & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
		Salsa & 2006 & \xmark & ? & ? & ? & ? & ? & ?\\ \hline
		Tribler & 2008 & \xmark & \checkmark & \checkmark & ? & ? & ? & \xmark \\ \hline
		Torks & 2009 & \checkmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
		NISAN & 2009 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
    \end{longtable}
\end{center}
